Amortization of Sub-programs in Simulators

### 2019-08-27 paper/learning/notes.tex
updated
add basic abstract

  In this work we devleop both a formalism and framework for amortizing sub-programs
  in simulators leveraging state-of-the-art variational inference techniques.
  In many real world scenarios, simulators are deployed to model computationally expensive
  and hard, or expensive, to observe scenarios.
   These may represent a set of events, or a population of interacting agents.

   \end{abstract}

@@

However, to construct this hybrid procedure requires both substantial engineering contributions 
and a description of the mathematical framework for these non-standard probabilistic programs. 
We provide both of these in this paper. As to implement this in practice we are required to do the following:
 \begin{itemize}
    \item An automated training procedure for any given simulator.
    \item Extend the protocols of existing probabilistic programming systems that hijack simulators, to enable:
    \begin{enumerate} \item 1) Only the necessary raw samples from the desired rejection sampling addresses to be collected for training.
                       \item 2) A process at inference time that replaces those given addresses with a learnt surrogate.
    \end{enumerate}
    \item Finer grained control over the actual latent variables of interest, to avoid unnecessary memory consumption and ensure that inference problem encountered remain tractable.
  \end{itemize}

@@

Thus, we need a regression from $\phi_j \rightarrow P^{in}){a_j}(\phi_j) $.
We have access to pairs $\{\phi_j, \hat{P}^{in}_{a_j}(\phi_j)\}$ for which 
the expectation $\mathbb{E}[\hat{P}^{in}_{a_j}( \phi_j)| \phi_j] = P^{in}_{a_j} (\phi_j)$ where
$\hat{P}$ is \textbf{Play back convo to find out}

>>>>

  In this work we develop both a formalism and framework for amortizing sub-programs
  in simulators leveraging state-of-the-art probabilistic programming and variational inference techniques.
  In many real world scenarios, simulators are deployed to model computationally expensive
  and hard, or expensive, to observe scenarios.
  The simulators may represent a set of events, or a population of interacting agents. 
  Recent work by \citet{baydin2018efficient} provided a framework for converting event-based simulators 
  to probabilistic programs, without having to re-implement the simulator within a given probabilistic
  programming system (PPS).
  However, issues arise with both memory and inference when \emph{nested}, or sub-programs within the simulator are simulating 
  some random process. 
  We demonstrate that by amortizing such sub-programs not only do we significantly reduce memory consumption, but
  we also enable inference to be performed in a statistically valid framework. 
\end{abstract}

@@

However, to construct this hybrid procedure requires both substantial engineering contributions 
and a description of the mathematical framework for these non-standard probabilistic programs. 
We provide both of these in this paper. As to implement this in practice we are required to do the following:
 \begin{itemize}
  \item A mathematical framework to amortize sub-programs within simulators. 
    \item An automated training procedure for any given simulator.
    \item Extend the protocols of existing probabilistic programming systems that hijack simulators, 
    to enable only the necessary raw samples from the desired rejection sampling addresses to be collected for training.
    \item A process at inference time that replaces those given addresses with a learnt surrogate.
        % \item Finer grained control over the actual latent variables of interest, to avoid unnecessary memory consumption and ensure that inference problem encountered remain tractable.
  \end{itemize}

@@

Thus, we need a regression from $\phi_j \rightarrow P^{in}{a_j}(\phi_j) $.
We have access to pairs $\{\phi_j, \hat{P}^{in}_{a_j}(\phi_j)\}$ for which 
the expectation $\mathbb{E}[\hat{P}^{in}_{a_j}( \phi_j)| \phi_j] = P^{in}_{a_j} (\phi_j)$ where
$\hat{P}$ is \textbf{Play back convo to find out}
